Matching Bullets

### 2015-12-08 imaging-paper.Rnw
adding linetype to bullets

ggplot() + 
  geom_rect(aes(xmin = xmin, xmax = xmax, fill=factor(type)), ymin = -6, ymax=6.5,  data = lines, alpha=0.2, show.legend = FALSE) +
  theme(legend.position="bottom") +
  geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(lines, !match)) +
  geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(lines, match)) +
  ylim(c(-6,6.5)) + theme_bw() +
  geom_line(data=lofX, aes(x=y, y=l30, group=bullet, colour=bullet)) +
  scale_colour_brewer("", palette="Set1") +
  scale_fill_brewer("", palette="Set2", na.value=alpha("grey60", 0.5)) +
    theme(legend.position = c(1,1.2), legend.justification=c(1,1),
        legend.background = element_rect(fill=alpha('white', 0.4))) + 
  ylab(expression(paste("Crosscut values (in ",mu,"m)", sep=""))) +
  xlab("y")
@
    }
\end{subfigure}
\caption{\label{fig:match}Matching striation marks: smooth (a), identify peaks and valley (b), and match peaks and valleys between crosscuts (c).}
\end{figure}

>>>>

ggplot() + 
  geom_rect(aes(xmin = xmin, xmax = xmax, fill=factor(type)), ymin = -6, ymax=6.5,  data = lines, alpha=0.2, show.legend = FALSE) +
  theme(legend.position="bottom") +
  geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(lines, !match)) +
  geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(lines, match)) +
  ylim(c(-6,6.5)) + theme_bw() +
  geom_line(data=lofX, aes(x=y, y=l30, group=bullet, linetype=bullet)) +
#  scale_colour_brewer("", palette="Set1") +
  scale_linetype_discrete("") +
  scale_colour_manual("", values=cols) +
  scale_fill_brewer("", palette="Set2", na.value=alpha("grey60", 0.5)) +
    theme(legend.position = c(1,1.1), legend.justification=c(1,1),
        legend.background = element_rect(fill=alpha('white', 0.4))) + 
  ylab(expression(paste("Crosscut values (in ",mu,"m)", sep=""))) +
  xlab("y")
@
    }
\end{subfigure}
\caption{\label{fig:match}Matching striation marks: smooth (a), identify peaks and valley (b), and match peaks and valleys between crosscuts (c).}
\end{figure}
